---
title: "Exploration enrichment pathways with differentially expressed (DE) genes  between old versus young"
author: "Team Le Grand"
date: "`r format(Sys.time(),'%d %B,%Y')`"
output:
  rmarkdown::html_document:
    theme: lumen
    df_print : paged
    fig_width: 15
    fig_height: 12
    toc: true
    toc_float: true
params:
  tablePlot : NA
  tablePlottest : NA
  subset : NA
  TypeUnique : NA
  col1 : NA
  col2 : NA
  minCountNormalized : NA
  maxCountNormalized : NA
  minlogF : NA
  maxlogF : NA
  title : NA
  subtitle : NA
  numberGeneInPathway : NA
  tableLeadingEdge : NA
  Heatmplot : NA
   
---

<style type="text/css">

h1.title {
  background-color: #158cba;
  font-size: 34px;
  color: white;
}
h1 { /* Header 1 */
  background-color: #158cba;
  font-size: 23px;
    color: white;
}
h2 { /* Header 2 */
  background-color: #158cba ;
  font-size: 20px;
    color: white;
}
h3 { /* Header 3 */
  background-color: #158cba ;
  font-size: 14px;
    color: white;
}
tr:nth-child(even){background-color: #f2f2f2;}

tr:hover {background-color: #ddd;}

th {
  background-color: #84c1d8ff;
  color: white;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, rows.print=5)
```
```{r pathsLoads , echo=FALSE,warning=FALSE,message=FALSE }

library(tidyverse)
library(ComplexHeatmap)
library(msigdbr)
library(cowplot)
library(openxlsx)
library(htmlwidgets)
library(gridExtra)
library(rmarkdown)
library(kableExtra)
library(formattable)
library(knitr)
library(DT)
library(ggrepel)
library(ggnewscale)# for labels to point
 library(circlize)

```
# Pathway explored : `r str_replace_all(params$title, "_", " ") `

This pathway contain `r params$numberGeneInPathway ` genes.

In these `r params$numberGeneInPathway` genes for each day and cell type, they are not all expressed and they are not all  differentially expressed between old versus young. 

Inside these differents genes, there are (cf table below) number of genes DE significant with a major participation  in the enrichment (leadingEdge cal by fgsea filter by padj<0.05).

`r kbl(params$tableLeadingEdge)%>%kable_paper("striped") `


## Dynamic through conditions (day and type cell): `r params$subtitle`

--------



```{r DynamicPathways, echo=FALSE,warning=FALSE,message=FALSE, fig.show='asis'}

typebytime<-ggplot( params$tablePlot, aes(x=day,y=as.numeric(NES),fill=type,color=type,group=paste0(pathway,'_',type))) +
    geom_point(aes(alpha=0.7,size=12),show.legend = F)+
    ylab("NES")+
    geom_line()+
    geom_hline(yintercept = 0, color="black", linetype="dashed",lwd=0.5,slope=F)+
    scale_color_manual(name="Cell type",values=params$tablePlot %>% arrange(type) %>% select(color) %>% unique() %>% unlist() %>% as.character())+
    theme_linedraw()+ theme(axis.title= element_text(face="bold"),axis.text = element_text(face="bold",size=14))

typebytime

```

## Heatmap of the top 40 genes DE between old versus young{.tabset .tabset-fade .tabset-pills}
***

### Scale borned by min and max meancountnormalised and log2foldchange of all dataset


```{r Heatmap, echo=FALSE,warning=FALSE,message=FALSE, fig.show='asis'}

reactomeGSEAheatmap<-draw (params$Heatmplot[[1]], column_title = params$title,
                           heatmap_legend_side = "bottom", padding = unit(c(2, 2, 2, 6), "mm"))

```

### Scale free

```{r Heatmap2, echo=FALSE,warning=FALSE,message=FALSE, fig.show='asis'}

reactomeGSEAheatmap<-draw (params$Heatmplot[[2]], column_title = params$title,
                           heatmap_legend_side = "bottom", padding = unit(c(2, 2, 2, 6), "mm"))

```

## Expression of genes DE in this pathway through days and type cells for young versus old{.tabset .tabset-fade .tabset-pills}
***

### Scale borned by min and max meancountnormalised and log2foldchange of all dataset

```{r ExpressGenesPathways, echo=FALSE,warning=FALSE,message=FALSE, fig.show='asis'}
PlotGenelogFacrossDay <- ggplot(params$tablePlottest, aes(x=DayAge, y=log2(meanCountNormalized+1),  color=log2F, group=GeneDayType)) +
      scale_y_continuous(limits=c(params$minCountNormalized,params$maxCountNormalized),breaks = c(0,log2(10),log2(100),log2(1000),log2(10000)),labels=c("0",'10',"100","1000","10000")) + # fill=name allow to automatically dedicate a color for each group
      geom_line(aes(col=log2F)) +
      geom_point(aes(shape=age,col=log2F))+
      scale_color_gradient2(midpoint=0,  low="blue", mid="grey88",high="red", limits = c(params$minlogF,params$maxlogF))+
      new_scale("color") +
      facet_wrap(~type,dir = "v", ncol=1, labeller = labeller(type=params$TypeUnique)) +
      geom_text_repel(data=subset2,
                      aes(label=symbol,color=type),  size=5,min.segment.length =0, segment.size = .8,point.padding= 0.8, force=5, force_pull = 0.1, max.overlaps=15,show.legend=F)  +

      scale_color_manual(values = params$col2, name="Top 10 genes padj<0.05")+
      ylab("meanCountNormalized")+ggtitle(unique(params$tablePlottest$Pathway))+
      theme_linedraw()+ theme(strip.text  = element_text(size = 12 , face = "bold"),strip.background = element_rect(fill="grey"),panel.grid.major.x = element_line(color = "gray60", size = 0.8),axis.title= element_text(face="bold"),axis.text = element_text(face="bold",size=14))
  

g <- ggplot_gtable(ggplot_build(PlotGenelogFacrossDay))
    stripRowName <- which(grepl('strip', g$layout$name))
    k <- 1
    fills <- rev(col1)
    for (i in stripRowName) {
      j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
      g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
      k <- k+1
    }
grid::grid.draw(g)
```

### Scale free

```{r ExpressGenesPathways2, echo=FALSE,warning=FALSE,message=FALSE, fig.show='asis'}
PlotGenelogFacrossDay <- ggplot(params$tablePlottest, aes(x=DayAge, y=meanCountNormalized,  color=log2F, group=GeneDayType)) +
      scale_y_log10()+
      geom_line(aes(col=log2F)) +
      geom_point(aes(shape=age,col=log2F))+
      scale_color_gradient2(midpoint=0,  low="blue", mid="grey88",high="red")+
      new_scale("color") +
      facet_wrap(~type,dir = "v", ncol=1, labeller = labeller(type=params$TypeUnique)) +
      geom_text_repel(data=subset2,
                      aes(label=symbol,color=type),  size=5,min.segment.length =0, segment.size = .8,point.padding= 0.8, force=5, force_pull = 0.1, max.overlaps=15,show.legend=F)  +

      scale_color_manual(values = params$col2, name="Top 10 genes padj<0.05")+
      ylab("meanCountNormalized")+ggtitle(unique(params$tablePlottest$Pathway))+
      theme_linedraw()+ theme(strip.text  = element_text(size = 12 , face = "bold"),strip.background = element_rect(fill="grey"),panel.grid.major.x = element_line(color = "gray60", size = 0.8),axis.title= element_text(face="bold"),axis.text = element_text(face="bold",size=14))
  

g <- ggplot_gtable(ggplot_build(PlotGenelogFacrossDay))
    stripRowName <- which(grepl('strip', g$layout$name))
    k <- 1
    fills <- rev(col1)
    for (i in stripRowName) {
      j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
      g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
      k <- k+1
    }
grid::grid.draw(g)
```

## Info on genes DE in this pathway

----------

```{r TableInfoGenes, echo=FALSE,warning=FALSE,message=FALSE, fig.show='asis'}

tablePlotfilter<-params$tablePlottest  %>% arrange(symbol) %>% select(symbol,DayType,day,type,age,padj,log2F,meanCountNormalized) %>% pivot_wider(names_from = age, names_prefix = "meanCountNormalized_", values_from = meanCountNormalized)   
tablePlotfilter <- tablePlotfilter %>% select(symbol,DayType,day,type,padj,log2F,meanCountNormalized_Young,log2F,meanCountNormalized_Old)
DT::datatable(tablePlotfilter, filter = 'top', extensions = c('Select', 'SearchPanes'),options = list(dom = 'Pfrtip',columnDefs = list(list(searchPanes = list(show = FALSE), targets = 2:8 ))),selection = 'none')
```