---
title: "Exploration enrichment pathways with differentially expressed (DE) genes  between old versus young"
author: "Team Le Grand"
date: "`r format(Sys.time(),'%d %B,%Y')`"
output:
  rmarkdown::html_document:
    theme: lumen
    df_print : paged
    fig_width: 15
    fig_height: 12
    toc: true
    toc_float: true
params:
  title : NA
  d : NA
  t : NA
  GSEAsigni : NA
   
---

<style type="text/css">

h1.title {
  background-color: #158cba;
  font-size: 34px;
  color: white;
}
h1 { /* Header 1 */
  background-color: #158cba;
  font-size: 23px;
    color: white;
}
h2 { /* Header 2 */
  background-color: #158cba ;
  font-size: 20px;
    color: white;
}
h3 { /* Header 3 */
  background-color: #158cba ;
  font-size: 14px;
    color: white;
}
tr:nth-child(even){background-color: #f2f2f2;}

tr:hover {background-color: #ddd;}

th {
  background-color: #84c1d8ff;
  color: white;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, rows.print=5)
```
```{r pathsLoads , echo=FALSE,warning=FALSE,message=FALSE }

library(tidyverse)
library(ComplexHeatmap)
library(msigdbr)
library(cowplot)
library(openxlsx)
library(htmlwidgets)
library(gridExtra)
library(rmarkdown)
library(kableExtra)
library(formattable)
library(knitr)
library(DT)
library(ggrepel)
library(ggnewscale)# for labels to point
library(circlize)
library(circlepackeR) 
library(igraph)
library(ggraph)
library(data.tree)

odir <- "/home/bioinfo/BulkAnalysis_plusNetwork2/exam_INTER_conditions/static/"
analyse<-"analysis/AnalysisGSEA/"

hsl_color<-data.frame("ECs"=270,"FAPs"=56,"M1"=26,"M2"=327,"Neutro"=164,"sCs"=202)
```
#  `r str_replace_all(params$title,'_',' ') `

--------


Only pathways in upper letter are enriched in `r params$t ` `r params$d `.  


```{r DynamicPathways, echo=FALSE,warning=FALSE,message=FALSE, fig.show='asis'}
#data_nested_2=read.table( file=paste0( odir,analyse,d,'_',t,"/",d,'_',t, "_table_REACTOME_Hierachie.txt"),na.strings="")
data_nested_2=read.table( file=paste0( odir,analyse,params$d,'_',params$t,"/",params$d,'_',params$t, "_table_REACTOME_Hierachie.txt"))
data_nested_2[is.na(data_nested_2)] <- ""
data_nested_2$pathString <- paste("roots", data_nested_2$level1, data_nested_2$level2, data_nested_2$level3, data_nested_2$level4,data_nested_2$level5,data_nested_2$level6,data_nested_2$level7, data_nested_2$level8, data_nested_2$level9, data_nested_2$level10,data_nested_2$level11,data_nested_2$level12, sep = "/")
data_Node <-as.Node(data_nested_2)

      if (t ==""){
        p <- circlepackeR(data_Node, size = "value",color_min = paste0("hsl(56,80%,80%)"), color_max = paste0("hsl(341,30%,30%)"), width = 1800, height = 1000)
        
      }else{
      p <- circlepackeR(data_Node, size = "value",color_min = paste0("hsl(",hsl_color[[t]],",80%,80%)"), color_max = paste0("hsl(",hsl_color[[t]],",30%,30%)"), width = 1500, height = 1000)
      }
p
```

## Table Hierarchieof Pathway Enrichied in Gene DE 

--------

Only pathways in upper bold letter are enriched in `r params$t ` `r params$d `.  


```{r Heatmap, echo=FALSE,warning=FALSE,message=FALSE, fig.show='asis'}

data_nested_2=read.table( file=paste0( odir,analyse,params$d,'_',params$t,"/",params$d,'_',params$t, "_table_REACTOME_Hierachie.txt"))
pathwayCheck<-c("IN REACTOME HIERARCHIE","NOT IN REACTOME HIERARCHIE")
rowsupp<-c()
data_nested_2[is.na(data_nested_2)] <- ""
for(l in rownames(data_nested_2)){
  pathTF=F
  for (c in 13:1){
    if (data_nested_2[l,c]!= ""){
      if (data_nested_2[l,c] == toupper(data_nested_2[l,c])){
        if (pathTF == F){
          if (data_nested_2[l,c] %in% pathwayCheck){
            rowsupp<-c(rowsupp,l)
            data_nested_2[l,c]<-paste0('<b>',data_nested_2[l,c],'</b>')
            break
          }
        }
      data_nested_2[l,c]<-paste0('<b>',data_nested_2[l,c],'</b>')
      }
    pathTF=T
    pathwayCheck<-c(pathwayCheck,data_nested_2[l,c])
    }
  }
}
data_nested_3<-data_nested_2[-as.numeric(rowsupp),-14]
data_nested_3<-data_nested_3 %>% arrange(level1,level2,level3,level4,level5,level6,level7,level8,level9,level10,level11,level12,level13)
write.table(data_nested_3, file=paste0( odir,analyse,d,"_",t,"/",d,'_',t, "_table_REACTOME_Hierachie_.txt"))
    
DT::datatable(data_nested_3, filter = 'top', extensions = c('RowGroup','Select', 'SearchPanes'),options = list(rowGroup = list(dataSrc = c(1,2)),dom = 'Pfrtip',columnDefs = list(list(searchPanes = list(show = FALSE), targets = 3:13 ))),selection = 'none',escape = F)
```