---
title: "Dynamic_DEG_by_type_Cell"
author: "Team Le Grand"
date: "`r format(Sys.time(),'%d %B,%Y')`"
output:
  rmarkdown::html_document:
    theme: lumen
    df_print : paged
    fig_width: 10
    fig_height: 8
    toc: true
    toc_float: true
   
---

<style type="text/css">


h1.title {
  background-color: #158cba;
  font-size: 34px;
  color: white;
}
h1 { /* Header 1 */
  background-color: #158cba;
  font-size: 23px;
    color: white;
}
h2 { /* Header 2 */
  background-color: #158cba ;
  font-size: 20px;
    color: white;
}
h3 { /* Header 3 */
  background-color: #158cba ;
  font-size: 14px;
    color: white;
}
tr:nth-child(even){background-color: #f2f2f2;}

tr:hover {background-color: #ddd;}

th {
  background-color: #84c1d8ff;
  color: white;
}
</style>




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r pathsLoads , echo=FALSE,warning=FALSE,message=FALSE }

library(tidyverse)
library(ComplexHeatmap)
library(msigdbr)
library(cowplot)
library(treemap)
library(networkD3)
library(dplyr)
library(ggplot2)
library(hrbrthemes)
library(webshot)
library(htmlwidgets)
library(gridExtra)
library(rmarkdown)
library(kableExtra)
library(formattable)
library(openxlsx)
library(shiny)
library(prettydoc)
library(ggnewscale)
library(knitr)
library(DT)
library(reshape2)
home<-"/home/bioinfo/BulkAnalysis_plusNetwork2/"
odir <- "/home/bioinfo/BulkAnalysis_plusNetwork2/exam_INTER_conditions/static/"
resdir <-'analysis/DEGOnOneorMoreDays/'

analyse<-"analysis/DynamiqueDEGbytypeCell/"
pathcombinaisontable<-paste0(odir,analyse,"ListOfDynamicDEofGenes.xlsx")
pathcombinaisontableUPDOWN<-paste0(odir,analyse,"ListOfDynamicUpDownDEofGenes.xlsx")
#rmarkdown::render('ReportGeneDEsigni.rmd', output_dir = paste0(odir,analyse))

fullDEsta = readRDS(paste0(odir, "rds/shot_rds_full.rds"))
vectTypeCell <- c("Neutro","M2","M1","ECs","FAPs","sCs")
cellcolors = list("ECs"="#0072B2","FAPs"="#F0E442","M1" = "#D55E00","M2" =  "#CC79A7","Neutro" =  "#009E73","sCs" = "#56B4E9" )

signiDEgene <- fullDEsta %>% filter(padj<=0.05)
genes_df <- read.table(paste0(home,"data/genesinfo.csv"), sep="\t", header=T)
vectTypeCell <- c("Neutro","M2","M1","ECs","FAPs","sCs")
vectDay1<-c("D0","D2","D4","D7")
vectDay2<-c("D2","D4","D7")

```
# Found genes differentially expressed(DE) on one, or more days, for one type Cell
***
 On one type Cell, we observe the dynamic of expression for old mice in comparison to young across days - in muscle regeneration
  
  - For some gene, the difference between Old and Young are specific of one Day, on one step of muscle regeneration.
  - For some gene, the difference is always present, no specific of one step of regeneration.
  - For some gene, the age up his expression in some days and down in other day.

```{r caclcStat1, echo=FALSE,warning=FALSE,message=FALSE }

TotUniqueGene<-Reduce(`+`,lapply(unique(fullDEsta$type), function(t) filter(fullDEsta,type == t) %>% dplyr::select(id) %>% unlist() %>% as.character() %>% unique() %>% length()))
signiDEgene <- fullDEsta %>% filter(padj<=0.05)
TotUniqueGeneDE<-Reduce(`+`,lapply(unique(signiDEgene$type), function(t) filter(signiDEgene,type == t) %>% dplyr::select(id) %>% unlist() %>% as.character() %>% unique() %>% length()))
TotGeneDED0<-length(signiDEgene[signiDEgene$day == 'D0',]$id)
TotUniqueGeneDED0<-length(unique(signiDEgene[signiDEgene$day == 'D0',]$id))

padjofpathsDEsigni = array(NA, dim=c(4,6))
rownames(padjofpathsDEsigni) = unique(fullDEsta$day)
colnames(padjofpathsDEsigni) = unique(fullDEsta$type)

for (d in unique(fullDEsta$day)){
  for (n in unique(fullDEsta$type)){
    padjofpathsDEsigni[d, n] <- round(length(fullDEsta %>% filter(day == d & type == n & padj <=0.05) %>% dplyr::select(symbol)  %>% unlist() %>% unique())/TotUniqueGeneDE*100, digits = 1)
    if ( padjofpathsDEsigni[d, n] == 0 ){padjofpathsDEsigni[d, n]=NA}
  }
}
totalDay = padjofpathsDEsigni %>% rowSums(na.rm = TRUE)
toltalTypeCell = padjofpathsDEsigni %>% colSums(na.rm = TRUE)
totalDay = c(totalDay,"")
padjofpathsDEsigni = rbind(padjofpathsDEsigni, "PercentDEGSigniOnTyCell"= toltalTypeCell)
padjofpathsDEsigni = cbind(padjofpathsDEsigni, "PercentDEGSigniOnDay"= totalDay)


```

Here we explore this dynamic on gene DE with a good confidence (padj<=0.05) i.e. **`r round(TotUniqueGeneDE/TotUniqueGene*100, digits = 0)`%** of genes ( `r TotUniqueGeneDE` genes on `r TotUniqueGene`). We look at DE genes by cell type, remember that some genes are DE on several cell types i.e for D0 `r TotGeneDED0-TotUniqueGeneDED0` genes DE on several type cell and `r TotUniqueGeneDED0` genes DE on only one typeCell  (`r round((TotGeneDED0-TotUniqueGeneDED0)/TotGeneDED0*100, digits = 0)`% of gene DE sur several type cell in D0). 

Overall, these are the proportions of sinificative DEG genes.

`r kbl(padjofpathsDEsigni,row.names = TRUE)%>%kable_paper("striped")`


For all future analyses these proportions will be kept.
Graphics and tables are in **`r paste0(odir,analyse)`**


## Gene DE on only one condition
***
```{r PlotDEGonlyOneDay, fig.align='center', echo=FALSE, warning=FALSE , error=FALSE}
###  CALCULATE
# Found the distribution of genes significatifs on Days Conditions by type cell
# Visualization for genes DE on only 1 days 
#
# ====================== Calculate =============================
dataFrameTotal=data.frame(signiDEgene,nbDayDE=rep(0,length(signiDEgene$baseMean)),Dynamic=rep(0,length(signiDEgene$baseMean)))
daystable<-c()
celltypetable<-c()
weightNode<-c()
ViolinDay<-c()
ViolinCell<-c()
ViolinName<-c()
ViolinValue<-c()
for ( typeCell in vectTypeCell ) {
  #keep table with signi gene
  tempoSigniDEgene<- signiDEgene %>% filter(type==typeCell)
  #keep only uniqueID sort by days
  uniqueIdByDay = lapply(unique(tempoSigniDEgene$day), function(x) filter(tempoSigniDEgene, day == x) %>% dplyr::select(id) %>% unlist() %>% as.character())
  names(uniqueIdByDay) = unique(tempoSigniDEgene$day)
  #found all combinaison where one same gene is on 1 or 2 or 3 or 4 days 
  allcombinaison =ComplexHeatmap::make_comb_mat(uniqueIdByDay)
  #keep only gene DE one only one DAY
  Sup2Combi<-allcombinaison[comb_degree(allcombinaison) == 1]

  #prepare vector to plot
  Node_Target<-names(comb_size(Sup2Combi))
  num_combi<-1
  for ( name in Node_Target){
    #Make table
    particulName<-str_extract_all(name,boundary("character"))
    if ( length(particulName[[1]]) <4 ){ vectDay = vectDay2} else { vectDay = vectDay1 }
    for (i in 1:(length(particulName[[1]]))){
      if ( particulName[[1]][[i]] == "1" ){
        dayDE<-vectDay[i]
        daystable<-c(daystable,vectDay[i])
        celltypetable<-c(celltypetable, typeCell)
        weightNode<-c(weightNode,unname(comb_size(Sup2Combi)[num_combi]))
      }
    }
    for (idG in extract_comb(Sup2Combi,name) ){
      dataFrameTotal[dataFrameTotal$id == idG & dataFrameTotal$type == typeCell ,]$nbDayDE<-1
      dataFrameTotal[dataFrameTotal$id == idG  & dataFrameTotal$type == typeCell ,]$Dynamic<-dayDE
      ViolinDay<-c(ViolinDay,dayDE)
      ViolinCell<-c(ViolinCell,typeCell)
      ViolinName<-c(ViolinName,unname(comb_size(Sup2Combi)[num_combi]))
      ViolinValue<-c(ViolinValue,dataFrameTotal[dataFrameTotal$id == idG & dataFrameTotal$type == typeCell & dataFrameTotal$day == dayDE ,]$log2FoldChange)
    }
    num_combi=num_combi+ 1
  }
}
GeneDEuniqueCond <- data.frame(
  Days=daystable,
  CellType=celltypetable,
  nbGene=weightNode
)
#cellcolors = factor( c("#0072B2","#F0E442", "#D55E00","#CC79A7","#009E73", "#56B4E9"), levels=c("ECs","FAPs","M1" ,"M2","Neutro" ,"sCs") )
PlotDEGonlyOneDay<-ggplot(GeneDEuniqueCond, aes(Days,CellType,size=nbGene,color=CellType))+geom_point()+ scale_color_manual(values =c("#0072B2","#F0E442" ,"#D55E00","#CC79A7","#009E73","#56B4E9"))  +
  scale_y_discrete(limits=rev)+   theme_ipsum()
PlotDEGonlyOneDay
save_plot(paste0(odir,analyse,"PlotDEGOnlyOneD.png"),PlotDEGonlyOneDay,base_width = 4, base_height = 7)

Violindata<-data.frame(ViolinDay=ViolinDay,
                       ViolinCell=ViolinCell,
                       ViolinName=ViolinName,
                       ViolinValue=ViolinValue)
PlotDEGonlyOneDayVioline<-ggplot(Violindata, aes(x=ViolinCell ,y=ViolinValue, fill=ViolinCell)) + # fill=name allow to automatically dedicate a color for each group
  geom_jitter(shape=16, position=position_jitter(0.4), aes(color=ViolinCell,alpha=0.001), show.legend=F)+geom_violin(scale="count",aes(alpha=0.001),show.legend = c("alpha"=F))+
  scale_fill_manual(values =c("#0072B2","#F0E442" ,"#D55E00","#CC79A7","#009E73","#56B4E9"))+scale_color_manual(values =c("#0072B2","#F0E442" ,"#D55E00","#CC79A7","#009E73","#56B4E9"))+
  coord_flip() + scale_x_discrete(limits=rev) +facet_grid(cols=vars(ViolinDay), switch = "both") +
  theme(panel.grid.major=element_blank(),axis.text.x = element_text(angle = 45)) +ylab("log2FoldChange of Gene padj <0.05")+xlab("Type Cell") +
  theme_minimal()

save_plot(paste0(odir,analyse,"PlotDEGOnlyOneD.png"),PlotDEGonlyOneDay,base_width = 4, base_height = 7)
save_plot(paste0(odir,analyse,"PlotDEGonlyOneDayVioline.png"),PlotDEGonlyOneDay,base_width = 4, base_height = 7)

```
```{r caclcStat2, echo=FALSE,warning=FALSE,message=FALSE }
maxD0<-GeneDEuniqueCond[GeneDEuniqueCond$nbGene == max(GeneDEuniqueCond[GeneDEuniqueCond$Days == "D0",]$nbGene),]
maxD2<-GeneDEuniqueCond[GeneDEuniqueCond$nbGene == max(GeneDEuniqueCond[GeneDEuniqueCond$Days == "D2",]$nbGene),]
maxD4<-GeneDEuniqueCond[GeneDEuniqueCond$nbGene == max(GeneDEuniqueCond[GeneDEuniqueCond$Days == "D4",]$nbGene),]
maxD7<-GeneDEuniqueCond[GeneDEuniqueCond$nbGene == max(GeneDEuniqueCond[GeneDEuniqueCond$Days == "D7",]$nbGene),]
dataframeDEGonecond <- lapply(unique(dataFrameTotal$type), function(t) filter(dataFrameTotal,type == t) %>% filter(nbDayDE == 1))
nbUniqGeneDEonecond<-  Reduce(`+`,lapply(dataframeDEGonecond, function(d) unique(d$id) %>% length()))

nbUniqGeneDEonecondD0 <- Reduce(`+`,lapply(dataframeDEGonecond, function(d) filter(d,day == "D0") %>% dplyr::select(id) %>% unlist() %>% as.character() %>% unique() %>% length()))
nbUniqGeneDEonecondD2 <- Reduce(`+`,lapply(dataframeDEGonecond, function(d) filter(d,day == "D2") %>% dplyr::select(id) %>% unlist() %>% as.character() %>% unique() %>% length()))
nbUniqGeneDEonecondD4 <- Reduce(`+`,lapply(dataframeDEGonecond, function(d) filter(d,day == "D4") %>% dplyr::select(id) %>% unlist() %>% as.character() %>% unique() %>% length()))
nbUniqGeneDEonecondD7 <- Reduce(`+`,lapply(dataframeDEGonecond, function(d) filter(d,day == "D7") %>% dplyr::select(id) %>% unlist() %>% as.character() %>% unique() %>% length()))
tablePercentgeneDEonecond<- data_frame("D0"=c(nbUniqGeneDEonecondD0,
                                              round(nbUniqGeneDEonecondD0/nbUniqGeneDEonecond*100, digits =0)),
                                       "D2"=c(nbUniqGeneDEonecondD2,
                                              round(nbUniqGeneDEonecondD2/nbUniqGeneDEonecond*100, digits =0)),
                                       "D4"=c(nbUniqGeneDEonecondD4,
                                              round(nbUniqGeneDEonecondD4/nbUniqGeneDEonecond*100, digits =0)),
                                       "D7"=c(nbUniqGeneDEonecondD7,
                                              round(nbUniqGeneDEonecondD7/nbUniqGeneDEonecond*100, digits =0)),
                                       "names"=c("Number Gene DE on Only one TypeCell","Percent Gene DE on Only one TypeCell")
)
tablePercentgeneDEonecond=column_to_rownames(tablePercentgeneDEonecond, var = "names")  
save_plot(paste0(odir,analyse,"PlotDEGOnlyOneD.png"),PlotDEGonlyOneDay,base_width = 4, base_height = 7)
```

There are `r round((nbUniqGeneDEonecond)/TotUniqueGeneDE*100, digits = 0)`% genes DE specific on only one day.

`r kbl(tablePercentgeneDEonecond,row.names = TRUE)%>%kable_paper("striped")`

Genes differentials expressed (DE) only in **physiology state (D0)** are max in  **`r maxD0$CellType`**. 
For Days post injury, In the **start of the regeneration** the genes DE only in D2 are max in **`r maxD2$CellType`**.
And for the **end of regeneration** in D4 and D7 the genes DE only in D4 are in **`r maxD4$CellType`** and only in D7 in **`r maxD7$CellType`**

`r kbl(rbind(maxD0,maxD2,maxD4,maxD7),row.names = FALSE)%>%kable_paper("striped") %>% add_header_above(c(" Type cell which the number od genes DE are maximum by Day"= 3))`


***

```{r PlotDEGonlyOneDayUPDOWM, fig.align='center',echo=FALSE}
dataFrameTotalUPDOWN=data.frame(signiDEgene,nbDayDE=rep(0,length(signiDEgene$baseMean)),Dynamic=rep(0,length(signiDEgene$baseMean)))
for ( typeCell in vectTypeCell ) {
  tempoSigniDEgene<- signiDEgene %>% filter(type==typeCell)
  uniqueIdByDayUP = lapply(unique(tempoSigniDEgene$day), function(x) filter(tempoSigniDEgene, day == x)  %>% filter(log2FoldChange > 0) %>% dplyr::select(id) %>% unlist() %>% as.character())
  names(uniqueIdByDayUP) = unique(paste0(tempoSigniDEgene$day,"_UP"))
  uniqueIdByDayDOWN = lapply(unique(tempoSigniDEgene$day), function(x) filter(tempoSigniDEgene, day == x)  %>% filter(log2FoldChange < 0) %>% dplyr::select(id) %>% unlist() %>% as.character())
  names(uniqueIdByDayDOWN) = unique(paste0(tempoSigniDEgene$day,"_DOWN"))
  uniqueIdByDay<-c(uniqueIdByDayUP,uniqueIdByDayDOWN)
  #UpSetR::upset(UpSetR::fromList(uniqueIdByDay))
  allcombinaison =ComplexHeatmap::make_comb_mat(uniqueIdByDay)
  Sup2Combi<-allcombinaison[comb_degree(allcombinaison) == 1]
  Node_Target<-names(comb_size(Sup2Combi))
  num_combi<-1 #for refind number gene on this combinaison
  for ( name in Node_Target){
    particulName<-str_extract_all(name,boundary("character"))
    nbDay=length(particulName[[1]])/2
    if ( nbDay<4 ){ vectDay = vectDay2} else { vectDay = vectDay1 }
    for (i in 1:nbDay){
      if ( particulName[[1]][[i]] == "1" ){
        dayDE<-paste0(vectDay[i],"_UP")
      }else { if (particulName[[1]][[i+nbDay]] == "1"){
        dayDE<-paste0(vectDay[i],"_DOWN")
      }}
    } 
    num_combi=num_combi+ 1
    for (idG in extract_comb(Sup2Combi,name) ){
      dataFrameTotalUPDOWN[dataFrameTotalUPDOWN$id == idG & dataFrameTotalUPDOWN$type == typeCell ,]$nbDayDE<-1
      dataFrameTotalUPDOWN[dataFrameTotalUPDOWN$id == idG  & dataFrameTotalUPDOWN$type == typeCell ,]$Dynamic<-dayDE
    }
  }
}

PlotDEGonlyOneDayVioline
```

## Gene DE on more of one condition

<div>
.wrapper { 
    max-width: 960px; 
    padding: 0; 
    margin: 0 auto;
 }

.widgets article.widget { 
    margin-bottom: 10px;
     width: 100%; 
     height: 100%;
    float: left; 
}

```{r DEGMoreOneDay, fig.align='center' , echo=FALSE, warning=FALSE , message=FALSE}
###  CALCULATE
# Found the distribution of genes significatifs on Days Conditions by type cell
# Visualization with sankeyNetwork for genes DE on more 1 days
#
# ====================== Calculate =============================
sourceNode<-c()
targetNode<-c()
valueEdge<-c()
Nbconnection<-c()
for ( typeCell in vectTypeCell ) {
  tempoSigniDEgene<- signiDEgene %>% filter(type==typeCell)
  uniqueIdByDay = lapply(unique(tempoSigniDEgene$day), function(x) filter(tempoSigniDEgene, day == x) %>% dplyr::select(id) %>% unlist() %>% as.character())
  names(uniqueIdByDay) = unique(tempoSigniDEgene$day)
  #UpSetR::upset(UpSetR::fromList(uniqueIdByDay))
  allcombinaison =ComplexHeatmap::make_comb_mat(uniqueIdByDay)
  Sup2Combi<-allcombinaison[comb_degree(allcombinaison) >= 2]
  Node_Target<-names(comb_size(Sup2Combi))
  num_combi<-1
  for ( name in Node_Target){
    particulName<-str_extract_all(name,boundary("character"))
    Nbconnection<-c(Nbconnection,rep(str_count(name,"1"),str_count(name,"1")-1))
    dayDE<-c()
    if ( length(particulName[[1]]) <4 ){ vectDay = vectDay2} else { vectDay = vectDay1 }
    for (i in 1:(length(particulName[[1]])-1)){
      if ( particulName[[1]][[i]] == "1" ){
        dayDE<-c(dayDE,vectDay[i])
        if ( particulName[[1]][[i+1]] == "1" ){
          sourceNode<-c(sourceNode,paste0(vectDay[i],"_",typeCell))
          targetNode<-c(targetNode,paste0(vectDay[i+1],"_",typeCell))
          valueEdge<-c(valueEdge,unname(comb_size(Sup2Combi)[num_combi]))
          dayDE<-c(dayDE,vectDay[i+1])
        }
        else {
          if (i+2 <= length(particulName[[1]]) && particulName[[1]][[i+2]] == "1"){
            sourceNode<-c(sourceNode,paste0(vectDay[i],"_",typeCell))
            targetNode<-c(targetNode,paste0(vectDay[i+2],"_",typeCell))
            valueEdge<-c(valueEdge,unname(comb_size(Sup2Combi)[num_combi]))
            dayDE<-c(dayDE,vectDay[i+2])
          }
          else {
            if(i+3 <= length(particulName[[1]]) && particulName[[1]][[i+3]] == "1"){
              sourceNode<-c(sourceNode,paste0(vectDay[i],"_",typeCell))
              targetNode<-c(targetNode,paste0(vectDay[i+3],"_",typeCell))
              valueEdge<-c(valueEdge,unname(comb_size(Sup2Combi)[num_combi]))
              dayDE<-c(dayDE,vectDay[i+3])
            }
          }
        }
      }
    }
    num_combi=num_combi+ 1
    for (idG in extract_comb(Sup2Combi,name) ){
      dataFrameTotal[dataFrameTotal$id == idG & dataFrameTotal$type == typeCell ,]$nbDayDE<-str_count(name,"1")
      dataFrameTotal[dataFrameTotal$id == idG  & dataFrameTotal$type == typeCell ,]$Dynamic<-str_c(unique(dayDE),collapse = ".")
    }
  }
} 

# Make a connection data frame
sourceNode<-c(sourceNode,"D0_M2","D0_M1")
targetNode<-c(targetNode,"D2_M2","D2_M1")
valueEdge<-c(valueEdge,0,0)
Nbconnection<-c(Nbconnection,0,0)
links <- data.frame(
  source=sourceNode,
  target=targetNode,
  value=valueEdge
)
# From these flows we need to create a node data frame: it lists every entities involved in the flow
nodes <- data.frame(
  name=c(as.character(links$source), as.character(links$target)) %>% 
    unique()
)
nodes$group <- as.factor(c(as.character(links$source), as.character(links$target)) %>% 
                           unique())
# With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1
links$group <- as.factor(Nbconnection)

# prepare color scale: I give one specific color for each node.
my_color <- 'd3.scaleOrdinal() .domain(["2","3","4","0","D0_ECs", "D2_ECs","D4_ECs","D7_ECs", "D0_FAPs", "D2_FAPs", "D4_FAPs","D7_FAPs","D0_sCs", "D2_sCs","D4_sCs","D7_sCs","D0_M1", "D2_M1","D4_M1","D0_M2" ,"D2_M2", "D4_M2","D7_M2"]) .range(["#D3DDDC","#C7B19C","#446455","white","#0072B2", "#0072B2" , "#0072B2", "#0072B2", "#F0E442", "#F0E442", "#F0E442", "#F0E442","#56B4E9","#56B4E9","#56B4E9","#56B4E9","#D55E00","#D55E00","#D55E00", "#CC79A7", "#CC79A7", "#CC79A7","#CC79A7"])'

# Make the Network. I call my colour scale with the colourScale argument
p <- sankeyNetwork(Links = links, Nodes = nodes, Source = "IDsource", Target = "IDtarget", 
                   Value = "value", NodeID = "name", colourScale=my_color, LinkGroup="group", NodeGroup="group", sinksRight = FALSE,
                   nodePadding=50, nodeWidth = 5,fontSize=10,iterations = 55,margin = list("right"=225), height = 650, width=1000)

my_hist<-ggplot(links,aes(value,fill = group))+geom_bar()+scale_fill_manual(values = c("white","#D3DDDC","#C7B19C","#446455"), name ="Number of Condtion DayPostInjury which Genes are DE" )
legend<-cowplot::get_legend(my_hist)
saveWidget(p, file=paste0(odir, analyse,"sankeyColor3.html"))
```
```{r caclcStat3, echo=FALSE,warning=FALSE,message=FALSE }
dataframeDEGtwocond <- lapply(unique(dataFrameTotal$type), function(t) filter(dataFrameTotal,type == t) %>% filter(nbDayDE == 2))
names(dataframeDEGtwocond)<-unique(dataFrameTotal$type)
nbUniqGeneDEtwocond<-  Reduce(`+`,lapply(dataframeDEGtwocond, function(d) unique(d$id) %>% length()))

dataframeDEGthreecond <- lapply(unique(dataFrameTotal$type), function(t) filter(dataFrameTotal,type == t) %>% filter(nbDayDE == 3))
names(dataframeDEGthreecond)<-unique(dataFrameTotal$type)
nbUniqGeneDEthreecond<-  Reduce(`+`,lapply(dataframeDEGthreecond, function(d) unique(d$id) %>% length()))

dataframeDEGfourcond <- lapply(unique(dataFrameTotal$type), function(t) filter(dataFrameTotal,type == t) %>% filter(nbDayDE == 4))
names(dataframeDEGfourcond)<-unique(dataFrameTotal$type)
nbUniqGeneDEfourcond<-  Reduce(`+`,lapply(dataframeDEGfourcond, function(d) unique(d$id) %>% length()))
tablePercentgeneDEacrosscond<- data_frame("one Day"= c(nbUniqGeneDEonecond,round(nbUniqGeneDEonecond/TotUniqueGeneDE*100,digits = 0)),
                                          "two Day"=c(nbUniqGeneDEtwocond,round(nbUniqGeneDEtwocond/TotUniqueGeneDE*100,digits = 0)),
                                          "three Day"=c(nbUniqGeneDEthreecond,round(nbUniqGeneDEthreecond/TotUniqueGeneDE*100, digits = 0)),
                                          "four Day"=c(nbUniqGeneDEfourcond, round(nbUniqGeneDEfourcond/TotUniqueGene*100, digits = 0)),
                                          "names"=c("Number Gene DE on ","Pourcent Gene DE on"))
tablePercentgeneDEacrosscond=column_to_rownames(tablePercentgeneDEacrosscond, var = "names")

i=0
for (t in dataframeDEGtwocond){ i=i+1 ; if (dim(t)[1] <1){ dataframeDEGtwocond<-dataframeDEGtwocond[-i] ; i=i-1 }}
i=0
for (t in dataframeDEGthreecond){ i=i+1; if (dim(t)[1] <1){dataframeDEGthreecond<-dataframeDEGthreecond[-i]; i=i-1}}
i=0
for (t in dataframeDEGfourcond){ i=i+1; if (dim(t)[1] <1){dataframeDEGfourcond<-dataframeDEGfourcond[-i]; i=i-1}}

maxGE2cond<-lapply(names(dataframeDEGtwocond), function(x) dataframeDEGtwocond[[x]] %>% dplyr::select(Dynamic) %>% unlist() %>% as.character() %>% table() %>% as_data_frame() %>% top_n(1) %>% mutate(n,"numberGene"=n/2))
names(maxGE2cond) = names(dataframeDEGtwocond)
maxGE3cond<-lapply(names(dataframeDEGthreecond), function(x) dataframeDEGthreecond[[x]] %>% dplyr::select(Dynamic) %>% unlist() %>% as.character() %>% table() %>% as_data_frame() %>% top_n(1) %>% mutate(n,"numberGene"=n/3))
names(maxGE3cond) = names(dataframeDEGthreecond)
maxGE4cond<-lapply(names(dataframeDEGfourcond), function(x) dataframeDEGfourcond[[x]] %>% dplyr::select(Dynamic) %>% unlist() %>% as.character() %>% table() %>% as_data_frame() %>% top_n(1) %>% mutate(n,"numberGene"=n/4))
names(maxGE4cond) = names(dataframeDEGfourcond)
tableMaxGE<-data_frame("ECs.Dynamics"=c(maxGE2cond$ECs$.,maxGE3cond$ECs$.,maxGE4cond$ECs$.),
                       "ECs.number"=c(maxGE2cond$ECs$numberGene,maxGE3cond$ECs$numberGene,maxGE4cond$ECs$numberGene),
                       "FAPs.Dynamics"=c(maxGE2cond$FAPs$.,maxGE3cond$FAPs$.,maxGE4cond$FAPs$.),
                       "FAPs.number"=c(maxGE2cond$FAPs$numberGene,maxGE3cond$FAPs$numberGene,maxGE4cond$FAPs$numberGene),
                       "sCs.Dynamics"=c(maxGE2cond$sCs$. ,maxGE3cond$sCs$.,maxGE4cond$sCs$.),
                       "sCs.number"=c(maxGE2cond$sCs$numberGene,maxGE3cond$sCs$numberGene,maxGE4cond$sCs$numberGene),
                       "M2.Dynamics"=c(maxGE2cond$M2$.,maxGE3cond$M2$.,NA),
                       "M2.number"=c(maxGE2cond$M2$numberGene,maxGE3cond$M2$numberGene,NA),
                       "M1.Dynamics"=c(maxGE2cond$M1$.,NA,NA),
                       "M1.number"=c(maxGE2cond$M1$numberGene,NA,NA),
)
```


`r kable(tablePercentgeneDEacrosscond,row.names = TRUE)%>% kable_paper("striped")`



```{r PlotDEGMoreOneDay, fig.align='center', echo=FALSE , warning=FALSE}
p
grid.arrange(legend)

kbl(as.tibble(tableMaxGE),align = "cccccccccc") %>%
  kable_paper("striped") %>%
  add_header_above(c( "ECs" = 2, "FAPs" = 2, "sCs" = 2, "M2"=2,"M1"=2)) %>%
  add_header_above(c(" On each combinaison Days, genes are maximum DE "= 10))

```
The DE genes over 2 or 3 days are predominantly expressed by the sCs. 
DE genes on 4 days are predominantly expressed by the FAPs  

Expression of FAPs are physiologically the most impacted by age. i.e for genes DE on 2 days, it's days 0 and 7 the most impacted
For ECs the impact of age is most focused on the end of regeneration D4 et D7, the return to normal.
For sCs the impact it's focus in start of regeneration D2 and D4


***

Now we try to see if genes DE on more of two condition are always UP regulated with age or DOWN or if the DE dynamic change between days.

```{r PlotDEGmoreOneDayUPDOWM, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center', out.height="100%",out.width="100%"}
###  CALCULATE
# Found the distribution of genes significatifs on Days Conditions by type cell
# Visualization with sankeyNetwork for genes DE on 2 conditions, 3 or 4 conditions, look afters contrast Up Down
#
# ====================== Calculate =============================
#1 Extract significative genes
#Fill dataFrameTotalUPDOWN
for ( typeCell in vectTypeCell ) {
  tempoSigniDEgene<- signiDEgene %>% filter(type==typeCell)
  uniqueIdByDayUP = lapply(unique(tempoSigniDEgene$day), function(x) filter(tempoSigniDEgene, day == x)  %>% filter(log2FoldChange > 0) %>% dplyr::select(id) %>% unlist() %>% as.character())
  names(uniqueIdByDayUP) = unique(paste0(tempoSigniDEgene$day,"_UP"))
  uniqueIdByDayDOWN = lapply(unique(tempoSigniDEgene$day), function(x) filter(tempoSigniDEgene, day == x)  %>% filter(log2FoldChange < 0) %>% dplyr::select(id) %>% unlist() %>% as.character())
  names(uniqueIdByDayDOWN) = unique(paste0(tempoSigniDEgene$day,"_DOWN"))
  uniqueIdByDay<-c(uniqueIdByDayUP,uniqueIdByDayDOWN)
  allcombinaison =ComplexHeatmap::make_comb_mat(uniqueIdByDay)
  Sup2Combi<-allcombinaison[comb_degree(allcombinaison) >= 2]
  Node_Target<-names(comb_size(Sup2Combi))
  CombNameAssocName<-set_name(Sup2Combi)
  nbDay=length(CombNameAssocName)/2
  for ( name in Node_Target){
    particulName<-str_extract_all(name,boundary("character"))
    dayDE<-c()
    if ( nbDay <4 ){ vectDay = vectDay2} else { vectDay = vectDay1 }
    if (particulName[[1]][1] == "1"){
      dayDE<-c(dayDE,paste0(vectDay[1],"_UP"))
    }else {if (particulName[[1]][1+nbDay] == "1" ){
      dayDE<-c(dayDE,paste0(vectDay[1],"_DOWN"))}}
    if (nbDay != 2){
      for(i in 2:(nbDay-1)){
        if (particulName[[1]][i] == "1"){
          dayDE<-c(dayDE,paste0(vectDay[i],"_UP"))
        }else {if (particulName[[1]][i+nbDay] == "1" ){
          dayDE<-c(dayDE,paste0(vectDay[i],"_DOWN"))}
        }}}
    else{i=1}
    if (particulName[[1]][nbDay] == "1"){
      dayDE<-c(dayDE,paste0(vectDay[nbDay],"_UP"))
    }else {if (particulName[[1]][i+nbDay+1] == "1" ){
      dayDE<-c(dayDE,paste0(vectDay[nbDay],"_DOWN"))}}
    for (idG in extract_comb(Sup2Combi,name) ){
      dataFrameTotalUPDOWN[dataFrameTotalUPDOWN$id == idG & dataFrameTotalUPDOWN$type == typeCell ,]$nbDayDE<-str_count(name,"1")
      dataFrameTotalUPDOWN[dataFrameTotalUPDOWN$id == idG  & dataFrameTotalUPDOWN$type == typeCell ,]$Dynamic<-str_c(unique(dayDE),collapse = ".")
      }
  }
}
#Prepare vector for plot + plot
dynamique <- function(tableSigni,vectTypeCell,outputprefix,oneTypeCell){
  sourceNode<-c()
  targetNode<-c()
  valueEdge<-c()
  groupetypeCell<-c()
  Nbconnection<-c()
  for ( typeCell in vectTypeCell ) {
    tempoSigniDEgene<- tableSigni %>% filter(type==typeCell)
    uniqueIdByDayUP = lapply(unique(tempoSigniDEgene$day), function(x) filter(tempoSigniDEgene, day == x)  %>% filter(log2FoldChange > 0) %>% dplyr::select(id) %>% unlist() %>% as.character())
    names(uniqueIdByDayUP) = unique(paste0(tempoSigniDEgene$day,"_UP"))
    uniqueIdByDayDOWN = lapply(unique(tempoSigniDEgene$day), function(x) filter(tempoSigniDEgene, day == x)  %>% filter(log2FoldChange < 0) %>% dplyr::select(id) %>% unlist() %>% as.character())
    names(uniqueIdByDayDOWN) = unique(paste0(tempoSigniDEgene$day,"_DOWN"))
    uniqueIdByDay<-c(uniqueIdByDayUP,uniqueIdByDayDOWN)
    allcombinaison =ComplexHeatmap::make_comb_mat(uniqueIdByDay)
    Sup2Combi<-allcombinaison[comb_degree(allcombinaison) >= 2]
    Node_Target<-names(comb_size(Sup2Combi))
    CombNameAssocName<-set_name(Sup2Combi)
    nbDay=length(CombNameAssocName)/2
    names(CombNameAssocName)<-seq(1,length(set_size(Sup2Combi)))
    num_combi<-1
    for ( name in Node_Target){
      particulName<-str_extract_all(name,boundary("character"))
      groupetypeCell<-c(groupetypeCell,rep(typeCell,nbDay-1))
      Nbconnection<-c(Nbconnection,rep(str_count(name,"1"),nbDay-1))
      if ( nbDay <4 ){ vectDay = vectDay2} else { vectDay = vectDay1 }
      if (particulName[[1]][1] == "1"){
        sourceNode<-c(sourceNode,paste0(vectDay[1],"_UP"))
      }else {if (particulName[[1]][1+nbDay] == "1" ){
        sourceNode<-c(sourceNode,paste0(vectDay[1],"_DOWN"))}
      else { 
        sourceNode<-c(sourceNode,paste0(vectDay[1],"_NODIFF"))
        }}
      if (nbDay != 2){
      for(i in 2:(nbDay-1)){
        namespl<-str_split(CombNameAssocName[i],'_')
        if (particulName[[1]][i] == "1"){
          sourceNode<-c(sourceNode,paste0(vectDay[i],"_UP"))
          targetNode<-c(targetNode,paste0(vectDay[i],"_UP"))
          valueEdge<-c(valueEdge,unname(comb_size(Sup2Combi)[num_combi]))
        }else {if (particulName[[1]][i+nbDay] == "1" ){
          sourceNode<-c(sourceNode,paste0(vectDay[i],"_DOWN"))
          targetNode<-c(targetNode,paste0(vectDay[i],"_DOWN"))
          valueEdge<-c(valueEdge,unname(comb_size(Sup2Combi)[num_combi]))}
        else { 
          sourceNode<-c(sourceNode,paste0(vectDay[i],"_NODIFF"))
          targetNode<-c(targetNode,paste0(vectDay[i],"_NODIFF"))
          valueEdge<-c(valueEdge,unname(comb_size(Sup2Combi)[num_combi]))}
        }}}
      else{i=1}
      if (particulName[[1]][nbDay] == "1"){
        targetNode<-c(targetNode,paste0(vectDay[nbDay],"_UP"))
        valueEdge<-c(valueEdge,unname(comb_size(Sup2Combi)[num_combi]))
      }else {if (particulName[[1]][i+nbDay+1] == "1" ){
        targetNode<-c(targetNode,paste0(vectDay[nbDay],"_DOWN"))
        valueEdge<-c(valueEdge,unname(comb_size(Sup2Combi)[num_combi]))}
      else { 
        targetNode<-c(targetNode,paste0(vectDay[nbDay],"_NODIFF"))
        valueEdge<-c(valueEdge,unname(comb_size(Sup2Combi)[num_combi]))}
      }
      num_combi=num_combi+ 1
    }
}
  # Make a connection data frame
  if (oneTypeCell == TRUE){
    links <- data.frame(
      source=sourceNode,
      target=targetNode,
      value=valueEdge,
      group=Nbconnection
    )
    links<-  aggregate(links$value,by=list("source"=links$source,"target"=links$target,"group"=links$group),FUN=sum)
    # From these flows we need to create a node data frame: it lists every entities involved in the flow
    nodes <- data.frame(
      name=c(as.character(links$source), as.character(links$target)) %>% 
        unique()
    )
    nodes$group <- as.factor(c(as.character(links$source), as.character(links$target)) %>% 
                               unique())
    # With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
    links$IDsource <- match(links$source, nodes$name)-1 
    links$IDtarget <- match(links$target, nodes$name)-1
    links$group <- as.factor(links$group)
    # prepare color scale: I give one specific color for each node.
    my_color <- 'd3.scaleOrdinal() .domain(["2","3","4","0",
    "D0_UP", "D2_UP","D4_UP","D7_UP", "D0_DOWN", "D2_DOWN", "D4_DOWN","D7_DOWN","D0_NODIFF", "D2_NODIFF","D4_NODIFF","D7_NODIFF",]) .range(
    ["#D3DDDC","#C7B19C","#446455","white","red","red","red","red","blue","blue","blue","blue","pink","pink","pink","pink"])'
    
  }else{
  links <- data.frame(
    source=sourceNode,
    target=targetNode,
    value=valueEdge,
    group=groupetypeCell
  )
  links<-  aggregate(links$value,by=list("source"=links$source,"target"=links$target,"group"=links$group),FUN=sum)
  # From these flows we need to create a node data frame: it lists every entities involved in the flow
  nodes <- data.frame(
    name=c(as.character(links$source), as.character(links$target)) %>% 
      unique()
  )
  nodes$group <- as.factor(c(as.character(links$source), as.character(links$target)) %>% 
                             unique())
  # With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
  links$IDsource <- match(links$source, nodes$name)-1 
  links$IDtarget <- match(links$target, nodes$name)-1
  links$group <- as.factor(links$group)
  # prepare color scale: I give one specific color for each node.
  
  my_color <- 'd3.scaleOrdinal() .domain([
  "D0_UP", "D2_UP","D4_UP","D7_UP", "D0_DOWN", "D2_DOWN", "D4_DOWN","D7_DOWN","D0_NODIFF", "D2_NODIFF","D4_NODIFF","D7_NODIFF",
  "ECs", "FAPs","sCs","M1", "M2"]) 
  .range(["red","red","red","red","blue","blue","blue","blue","pink","pink","pink","pink","#0072B2","#F0E442","#56B4E9","#D55E00","#CC79A7"])'
  # 
  # Make the Network. I call my colour scale with the colourScale argument
  
  }
  
  p <- sankeyNetwork(Links = links, Nodes = nodes, Source = "IDsource", Target = "IDtarget", 
                     Value = "x", NodeID = "name", colourScale=my_color, LinkGroup="group", NodeGroup="group", sinksRight = FALSE,
                     nodePadding=50, nodeWidth = 5,fontSize=10,iterations = 55,margin = list("right"=225), height = 650, width=1000)
  p
  saveWidget(p, file=paste0(odir, analyse,outputprefix,"sankeyColorUPDOWN.html"))
  webshot(paste0(odir,analyse,outputprefix, "sankeyColorUPDOWN.html"), paste0(odir,analyse,outputprefix,"sankeyCollorUPDOWN.png"), delay = 0.2)
  return(p)
}

my_hist<-ggplot(signiDEgene,aes(baseMean,fill = type))+geom_bar()+scale_fill_manual(values = cellcolors, name ="Type Cell" )
legend<-cowplot::get_legend(my_hist)
palltypecell<-dynamique(signiDEgene,vectTypeCell,"AlltypeCell",FALSE)
palltypecell
grid.arrange(legend)
```
```{r caclcStat4, echo=FALSE,warning=FALSE,message=FALSE }
psCs<-dynamique(signiDEgene,"sCs","sCs",TRUE)
pECs<-dynamique(signiDEgene,"ECs","ECs",TRUE)
pFAPs<-dynamique(signiDEgene,"FAPs","FAPs",TRUE)
pM2<-dynamique(signiDEgene,"M2","M2",TRUE)
pM1<-dynamique(signiDEgene,"M1","M1",TRUE)

daysv<-list()
daysv$ECs=c("D0","D2","D4","D7")
daysv$FAPs<-c("D0","D2","D4","D7")
daysv$M1<-c("D2","D4")
daysv$M2<-c("D2","D4","D7")
daysv$Neutro<-c("D2")
daysv$sCs<-c("D0","D2","D4","D7")
Typecellv<-vectTypeCell <- c("ECs","FAPs","M1","M2","Neutro","sCs")

concatMeanCountNormalized<-function(age){
  tempoTable<-read.table(paste0(home,'data/meanCountNormalised_',age,'_D0.ECs.txt'))
  nbligne=length(tempoTable$GeneID)
  GeneID=tempoTable$GeneID
  age.meanCountNormalizedtable<-data_frame(tempoTable,type = rep("ECs",nbligne),days = rep("D0",nbligne))
  for ( t in Typecellv){
    for (day in daysv[[t]]){
      tempoTable<-read.table(paste0(home,'data/meanCountNormalised_',age,'_',day,'.',t,'.txt'))
      nbligne=length(tempoTable$GeneID)
      if(GeneID == tempoTable$GeneID){
        tempo<-data_frame(tempoTable,type = rep(t,nbligne),days = rep(day,nbligne))
        age.meanCountNormalizedtable<-rbind(age.meanCountNormalizedtable,tempo)
      }
    }
  }
  age.meanCountNormalizedtable <- age.meanCountNormalizedtable %>% mutate( symbol = genes_df[match(age.meanCountNormalizedtable$GeneID, genes_df$Geneid),]$symbol)
  age.meanCountNormalizedtable <- age.meanCountNormalizedtable %>% unite( 'GeneDayType' , symbol:days:type ,sep = '_',remove = F)
  return(age.meanCountNormalizedtable)
}

CountNormalizedYoung<-concatMeanCountNormalized('Young')
CountNormalizedOld<-concatMeanCountNormalized('Old')

dataFrameTotalUPDOWN <- dataFrameTotalUPDOWN %>% mutate(GeneDayType=paste0(symbol,'_',day,'_',type))

dataFrameTotalUPDOWN<- dataFrameTotalUPDOWN %>% mutate( meanCountNormalizedYoung =round(as.numeric(CountNormalizedYoung[match(dataFrameTotalUPDOWN$GeneDayType,CountNormalizedYoung$GeneDayType),]$countNormalized), digits=4) )
dataFrameTotalUPDOWN<- dataFrameTotalUPDOWN %>% mutate( meanCountNormalizedOld =round( as.numeric(CountNormalizedOld[match(dataFrameTotalUPDOWN$GeneDayType,CountNormalizedOld$GeneDayType),]$countNormalized),digits=4))
dataFrameTotalUPDOWN<-dataFrameTotalUPDOWN %>% mutate(log2FoldChange=round(log2FoldChange,digits = 4))


```

We can see somes tendances, like genes D0 DOWN regulated are few UP regulated in D2,
However genes D2 DOWN regulated are many to be UP regulated in D4.
For more visibility, we look the tendance typeCell by typeCell

## Muscle Stem Cell - Cellule satellite sCs

```{r PlotDEGmoreOneDayUPDOWNsCs, echo=FALSE, warning=FALSE}
psCs
tablefilter<-dataFrameTotalUPDOWN %>% filter(type=="sCs", nbDayDE > 1) %>% arrange(nbDayDE,Dynamic,symbol) %>% select(nbDayDE,Dynamic,symbol,id,day,type,padj,log2FoldChange,meanCountNormalizedYoung,meanCountNormalizedOld)
DT::datatable(tablefilter, filter = 'top', extensions = c('RowGroup','Select', 'SearchPanes'),options = list(rowGroup = list(dataSrc = c(1,2)),dom = 'Pfrtip',columnDefs = list(list(searchPanes = list(show = FALSE), targets = 3:9 ))),selection = 'none',escape = F,rownames=F)
```

## Endothelial Cell - ECs

```{r PlotDEGmoreOneDayUPDOWNECs, echo=FALSE, warning=FALSE}
pECs
tablefilter<-dataFrameTotalUPDOWN %>% filter(type=="ECs", nbDayDE > 1) %>% arrange(nbDayDE,Dynamic,symbol) %>% select(nbDayDE,Dynamic,symbol,id,day,type,padj,log2FoldChange,meanCountNormalizedYoung,meanCountNormalizedOld)
DT::datatable(tablefilter, filter = 'top', extensions = c('RowGroup','Select', 'SearchPanes'),options = list(rowGroup = list(dataSrc = c(1,2)),dom = 'Pfrtip',columnDefs = list(list(searchPanes = list(show = FALSE), targets = 3:9 ))),selection = 'none',escape = F,rownames=F)
```

## FibroAdipogenic Progenitors - FAPs

```{r PlotDEGmoreOneDayUPDOWNFAPs, echo=FALSE, warning=FALSE}
pFAPs
tablefilter<-dataFrameTotalUPDOWN %>% filter(type=="FAPs", nbDayDE > 1) %>% arrange(nbDayDE,Dynamic,symbol) %>% select(nbDayDE,Dynamic,symbol,id,day,type,padj,log2FoldChange,meanCountNormalizedYoung,meanCountNormalizedOld) 
DT::datatable(tablefilter, filter = 'top', extensions = c('RowGroup','Select', 'SearchPanes'),options = list(rowGroup = list(dataSrc = c(1,2)),dom = 'Pfrtip',columnDefs = list(list(searchPanes = list(show = FALSE), targets = 3:9 ))),selection = 'none',escape = F,rownames=F)
```

## Macrophage 2 - M2

```{r PlotDEGmoreOneDayUPDOWNM2, echo=FALSE, warning=FALSE}
pM2

tablefilter<-dataFrameTotalUPDOWN %>% filter(type=="M2", nbDayDE > 1) %>% arrange(nbDayDE,Dynamic,symbol) %>% select(nbDayDE,Dynamic,symbol,id,day,type,padj,log2FoldChange,meanCountNormalizedYoung,meanCountNormalizedOld) 
DT::datatable(tablefilter, filter = 'top', extensions = c('RowGroup','Select', 'SearchPanes'),options = list(rowGroup = list(dataSrc = c(1,2)),dom = 'Pfrtip',columnDefs = list(list(searchPanes = list(show = FALSE), targets = 3:9 ))),selection = 'none',escape = F,rownames=F)
```

## Macrophage 1 - M1

```{r PlotDEGmoreOneDayUPDOWNM1, echo=FALSE, warning=FALSE}
pM1
tablefilter<-dataFrameTotalUPDOWN %>% filter(type=="M1", nbDayDE > 1) %>% arrange(nbDayDE,Dynamic,symbol) %>% select(nbDayDE,Dynamic,symbol,id,day,type,padj,log2FoldChange,meanCountNormalizedYoung,meanCountNormalizedOld) 
DT::datatable(tablefilter, filter = 'top', extensions = c('RowGroup','Select', 'SearchPanes'),options = list(rowGroup = list(dataSrc = c(1,2)),dom = 'Pfrtip',columnDefs = list(list(searchPanes = list(show = FALSE), targets = 3:9 ))),selection = 'none',escape = F,rownames=F)
```

</div>

# HEAD Table recapitulatif


```{r HeadBilanTable, echo=FALSE, warning=FALSE}
countNbConditionGeneDE<-dataFrameTotalUPDOWN  %>% dplyr::count(symbol,sort = T)
tablefilter<-dataFrameTotalUPDOWN  %>% mutate(n= countNbConditionGeneDE[match(dataFrameTotalUPDOWN$symbol,countNbConditionGeneDE$symbol),]$n ) %>% arrange(desc(n),symbol,desc(nbDayDE),Dynamic) %>% select(symbol,nbDayDE,Dynamic,id,day,type,padj,log2FoldChange,meanCountNormalizedYoung,meanCountNormalizedOld) 
DT::datatable(tablefilter, filter = 'top', extensions = c('RowGroup','Select', 'SearchPanes'),options = list(rowGroup = list(dataSrc = c(1,2,3)),dom = 'Pfrtip',columnDefs = list(list(searchPanes = list(show = FALSE), targets = 4:9 ))),selection = 'none',escape = F,rownames=F)
```