---
title: "Ageing impact in gene expression on skeletal muscle repair"
subtitle: "Bioinformatic analysis : differential expression genes part"
author: "Team Le Grand"
date: "`r format(Sys.time(),'%d %B,%Y')`"
output:
  rmarkdown::html_document:
    theme: lumen
    df_print : paged
    fig_width: 10
    fig_height: 8

   
---

<style type="text/css">


h1.title {
  background-color: #158cba;
  font-size: 34px;
  color: white;
}
h1 { /* Header 1 */
  background-color: #158cba;
  font-size: 23px;
    color: white;
}
h2 { /* Header 2 */
  background-color: #158cba ;
  font-size: 20px;
    color: white;
}
h3 { /* Header 3 */
  background-color: #158cba ;
  font-size: 14px;
    color: white;
}
tr:nth-child(even){background-color: #f2f2f2;}

tr:hover {background-color: #ddd;}

th {
  background-color: #84c1d8ff;
  color: white;
}

.btn {
    border-width: 0 0px 0px 0px;
    font-weight: normal;
    text-transform: ;
}
.btn-default {
    color: #2ecc71;
    background-color: #ffffff;
    border-color: #ffffff;
}

</style>

[linksAnalysisDEG](./GeneDEsigniOnMoreOneTimePoint.html)

```{r pathsLoads , echo=FALSE,warning=FALSE,message=FALSE }
library(tidyverse)
library(ComplexHeatmap)
library(msigdbr)
library(cowplot)
library(treemap)
library(networkD3)
library(dplyr)
library(ggplot2)
library(hrbrthemes)
library(webshot)
library(htmlwidgets)
library(gridExtra)
library(kableExtra)
library(RColorBrewer)
library(facetious)
library(formattable)
library(grid)
library(PantaRhei)
library(DT)
library(reshape2)
odir <- "~/BulkAnalysis_plusNetwork/exam_INTER_conditions/static/"
pathcombinaisontableUPDOWN<-paste0(odir,"TableDEG/TableDynamicUpDownDEG")

dataFrameTotalUPDOWN<-readRDS(paste0(pathcombinaisontableUPDOWN,'.rds'))

countNbConditionGeneDE<-dataFrameTotalUPDOWN  %>% dplyr::count(symbol,sort = T)
tablefilter<-dataFrameTotalUPDOWN  %>% mutate(n= countNbConditionGeneDE[match(dataFrameTotalUPDOWN$symbol,countNbConditionGeneDE$symbol),]$n ) %>% arrange(desc(n),symbol,desc(nbDayDE),CombiDaysUpDown) %>% select(n,symbol,nbDayDE,CombiDaysUpDown,CombiDayDEG,NbUpDown,id,day,type,padj,log2FoldChange,meanCountNormalizedYoung,meanCountNormalizedOld) 
```

```{r tableResolvingUPDOWN, echo=FALSE, warning=FALSE}
DT::datatable(tablefilter, filter = 'top', extensions = c('RowGroup','Select', 'SearchPanes'),options = list(rowGroup = list(dataSrc = c(1,2,3,4)),dom = 'Pfrtip',columnDefs = list(list(searchPanes = list(show = FALSE), targets = 5:11 ))),selection = 'none',escape = F,rownames=F)
```

[linksAnalysisGSEA](./fgseaReport.html)

